\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-18 evaluation.tex
State the time taken to develop MigratingTable.

Modeling the Live Migration Table required \PDComment{waiting confirmation from
Matt}. The modeling effort was done in parallel with the development of the actual system. 
This is in contrast with the other two case studies discussed in this paper, where the modeling 
activity occurred independently and at a later stage of the development process.

>>>>

Developing the Live Migration Table and its \psharp test harness took about 5 weeks. The test harness was developed in parallel with the actual system.
This is in contrast with the other two case studies discussed in this paper, where the modeling 
activity occurred independently and at a later stage of the development process.
